---
title: "Tidy Tuesday - US Spending on Kids"
output: html_document
---

# Cleaning environment

```{r}
rm(list = ls())
```

# Tidy Tuesday setup

```{r}
library(tidytuesdayR)
library(tidyverse)
library(tidytext)
library(scales)
library(lubridate)
library(extrafont)

# font_import("C:\\Users\\USER\\AppData\\Local\\Microsoft\\Windows\\Fonts")
# font_import()
loadfonts()
loadfonts(device = "win")

theme_set(theme_bw())

tuesdata <- tt_load('2020-09-08')
friends_script <- tuesdata$friends
friends_info <- tuesdata$friends_info
friends_emotions <- tuesdata$friends_emotions
```

```{r}
friends <- 
  friends_script %>% 
  count(speaker, sort = TRUE) %>% 
  head(6) %>% 
  pull(speaker)

season_release <- 
  friends_info %>% 
  filter(episode == 1) %>%
  select(season, air_date)
```

# Analysing the friends' emotions

First I created a tibble that shows each friends text with the emotion it represents.

```{r}
joined_emotions <- 
  friends_emotions %>% 
  left_join(friends_script, by = c("season", "episode", "scene", "utterance")) %>% 
  filter(speaker %in% friends)
```

Then I analysed the frequency of emotions that each friend showed throughout the series.

```{r}
joined_emotions %>%
  add_count(speaker) %>% 
  group_by(speaker, emotion) %>% 
  summarise(ratio = n() / mean(n)) %>%
  ungroup() %>% 
  mutate(speaker = reorder_within(speaker, ratio, emotion)) %>%
  ggplot(aes(ratio, speaker)) +
    facet_wrap(~ emotion, scales = "free") +
    geom_col() +
    scale_y_reordered() +
    scale_x_continuous(labels = percent) +
    labs(x = "",
         y = "",
         title = "The one that shows the emotions of each friend") +
    theme(plot.title = element_text(family = "Gabriel Weiss' Friends Font"))
  
```

As expected, Phoebe seems to be the happiest friend (also the saddest one), while Rachel seems the friend that is most often mad (over 15% of the time she speeks!)

Now I want to analyse the evolution of each emotion throughout the series

```{r}
joined_emotions %>% 
  add_count(season, episode) %>% 
  group_by(season, episode, emotion) %>% 
  summarise(ratio = n() / mean(n)) %>% 
  left_join(friends_info, by = c("season", "episode")) %>% 
  ggplot(aes(air_date, ratio)) +
    geom_smooth(aes(color = emotion), se = FALSE) +
    geom_vline(xintercept = season_release$air_date, linetype = 3) +
    geom_text(aes(date, ratio, label = label), 
              data = tibble(date = as.Date(season_release$air_date[1:4] + dmonths(6)), 
                            ratio = .5, 
                            label = c("season 1",
                                      "season 2",
                                      "season 3",
                                      "season 4")),
              size = 4) +
    xlim(c(season_release$air_date[1], season_release$air_date[5])) +
    scale_y_continuous(labels = percent) +
    labs(x = "",
         y = "",
         color = "",
         title = "The one with emotions") +
    theme(plot.title = element_text(family = "Gabriel Weiss' Friends Font"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
```

Now I'll do the same analysis but separated by friend

```{r}
joined_emotions %>% 
  add_count(season, episode, speaker) %>%
  group_by(season, episode, emotion, speaker) %>% 
  summarise(ratio = n() / mean(n)) %>% 
  left_join(friends_info, by = c("season", "episode")) %>% 
  ggplot(aes(air_date, ratio)) +
    geom_smooth(aes(color = speaker), se = FALSE) +
    facet_wrap(~ emotion, scales = "free") +
    geom_vline(xintercept = season_release$air_date, linetype = 3) +
    geom_text(aes(date, ratio, label = label), 
              data = tibble(date = as.Date(season_release$air_date[1:4] + dmonths(6)), 
                            ratio = .05, 
                            label = c("season 1",
                                      "season 2",
                                      "season 3",
                                      "season 4")),
              size = 4) +
    xlim(c(season_release$air_date[1], season_release$air_date[5])) +
    expand_limits(y = 0.04) +
    scale_y_continuous(labels = percent) +
    labs(x = "Air Date",
         y = "",
         color = "",
         title = "The one where the friends compare their emotions") +
    theme(plot.title = element_text(family = "Gabriel Weiss' Friends Font"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())

### 

joined_emotions %>% 
  add_count(season, episode, speaker) %>%
  group_by(season, episode, emotion, speaker) %>% 
  summarise(ratio = n() / mean(n)) %>% 
  left_join(friends_info, by = c("season", "episode")) %>% 
  ggplot(aes(air_date, ratio)) +
    geom_smooth(aes(color = emotion), se = FALSE) +
    facet_wrap(~ speaker, scales = "free") +
    geom_vline(xintercept = season_release$air_date, linetype = 3) +
    geom_text(aes(date, ratio, label = label), 
              data = tibble(date = as.Date(season_release$air_date[1:4] + dmonths(6)), 
                            ratio = 0, 
                            label = c("season 1",
                                      "season 2",
                                      "season 3",
                                      "season 4")),
              size = 4) +
    xlim(c(season_release$air_date[1], season_release$air_date[5])) +
    scale_y_continuous(labels = percent) +
    labs(x = "",
         y = "",
         color = "",
         title = "The one with the emotions of each friend throughout time") +
    theme(plot.title = element_text(family = "Gabriel Weiss' Friends Font"),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
```